

# Import packages


```{r}

library(tidyverse) # Dplyr and other packages
library(patchwork) # Combine separate ggplots
library(ggcorrplot) # Correlation plots
library(viridisLite) # Virids color scale
library(lmtest) # Tests for linear model
library(car) # Other test for linear model
library(caret) # Regression training
library(scales) # Custom scales
source("../objects_and_functions.R") # Helper objects and functions

```


# Read files


```{r}

# FFR Target Range - Lower limit
ffr_tarl <- read.csv("DFEDTARL.csv")
# FFR Target Range - Upper limit
ffr_taru <- read.csv("DFEDTARU.csv")

# Display data
head(ffr_tarl, 10)
head(ffr_taru, 10)


```


# Build a target range per year


```{r}

# Lower limit
ffr_lowest_tarl <- ffr_tarl %>%
  mutate(year = year(date(DATE))) %>% # Get year
  group_by(year) %>% # Group by year
  summarise(tarl = min(DFEDTARL)) # Lowest rate of each year

# Upper limit
ffr_highest_taru <- ffr_taru %>%
  mutate(year = year(date(DATE))) %>% # Get year
  group_by(year) %>% # Group by year
  summarise(taru = min(DFEDTARU)) # Highest rate of each year

# Join lower and upper limit set
ffr_set <- inner_join(ffr_lowest_tarl, ffr_highest_taru, "year") %>%
  mutate(
    tr_mid = apply(.[, c("tarl", "taru")], 1, mean), # Calculate the mid point of the target range for each year
    year = as.integer(year) # Change year to integer
  ) 

# Display the ffr set
ffr_set


```


# Plot the mid point of ffr's target range


```{r}


ffr_set %>%
  ggplot(aes(x = year, y = tr_mid)) +
  geom_line(color = color_pallete[2], linewidth = 1) + # Line graphic
  theme_classic() + # Main theme
  labs(
    title = "Annual FFR - Mid Point",
    x = "Year",
    y = "Mid Point %"
  ) + # Titles
  scale_x_continuous(breaks = ffr_set$year) + # Display all years
  scale_y_continuous(breaks = seq(0, 5, 1)) +
  qa_dark # Add theme settings


```

# Calculate the mid point with the raw data (every 7 days)


```{r}

ffr_set_full <- inner_join(ffr_tarl, ffr_taru, "DATE") %>%
  mutate(
    tr_mid = apply(.[, c("DFEDTARL", "DFEDTARU")], 1, mean),
    DATE = date(DATE)
  ) %>%
  rename(date = DATE) %>%
  select(date, tr_mid)

```


# Plot the mid point for the ffr's target range with the raw data


```{r}

p_ffr_set_full <- ffr_set_full %>%
  ggplot(aes(x = date, y = tr_mid)) +
  geom_line(color = color_pallete[3], linewidth = 1) + # Line graphic
  theme_classic() + # Main theme
  labs(
    title = "FFR - Mid Point",
    x = "Date",
    y = "Mid Point %"
  ) + # Titles
  scale_x_date(date_labels = "%Y-%m-%d", breaks = "12 months") + # Date labels scale
  scale_y_continuous(breaks = seq(0, 5, 1)) +
  qa_dark # Add theme settings

p_ffr_set_full

```


# Histogram analysis - FFR Series


```{r}

ffr_set_full %>%
  ggplot(aes(x = tr_mid, y = after_stat(count) * 100 / sum(count))) +
  geom_histogram(color = "white", fill = color_pallete[3], bins = 5) +
  theme_classic() + # Main theme
  labs(
    title = "FFR - Histogram",
    x = "FFR",
    y = "Freq %"
  ) + # Titles
  qa_dark + # Add theme settings
  theme(axis.text.x = element_text(angle = 0))

```

# FFR series - time division


```{r}

# The behavior of the series suggests that we may need a non conventional model to create a reliable forecast using only ffr's mid point data
p_ffr_set_full +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = "6 months") +
  geom_vline(xintercept = date("2016-11-30"), color = "white", linetype = "dotted", linewidth = 1) +
  geom_vline(xintercept = date("2020-03-01"), color = "white", linetype = "dotted", linewidth = 1) +
  geom_vline(xintercept = date("2022-03-01"), color = "white", linetype = "dotted", linewidth = 1)
  

```

# Import inflation data


```{r}

# Since the target range depend on inflation levels, it's important to know inflation's behavior

# Import CPI data
cpi_set <- read.csv("MEDCPI.csv")

# Full CPI set
cpi_set <- cpi_set %>%
  mutate(DATE = date(DATE)) %>%
  rename(cpi = MEDCPIM158SFRBCLE,
         date = DATE)

cpi_set

```


# Select first day of each month in FFR set


```{r}

# Select the first day of each month in FFR set
ffr_set_first_day <- ffr_set_full %>%
  mutate(
    year_and_month = year(date) * 100 + month(date),
    day = day(date)
  ) %>%
  group_by(year_and_month) %>%
  filter(day == min(day) & day == 1) %>%
  ungroup() %>%
  select(-all_of(c("day", "year_and_month")))

# Minimum date
min_date_ffr <- min(ffr_set_first_day$date)
# Maximum date
max_date_ffr <- max(ffr_set_first_day$date)


```


# FFR in the last 12 months


```{r}

ffr_set_first_day %>%
  arrange(desc(date)) %>%
  mutate(n = row_number()) %>%
  filter(n <= 12)

```



# Target variable: FFR's mid point in january 1st (12 months ahead)


```{r}

h <- 6

ffr_set_h6 <- ffr_set_first_day %>%
  filter(date >= min_date_ffr %m+% months(h)) %>%
  rename(tr_mid_h6 = tr_mid) %>%
  mutate(date = date %m-% months(h))

ffr_set_h6

```


# Add the target variable to the FFR set


```{r}

full_set <- ffr_set_first_day %>%
  filter(between(date, date("2022-03-01"), max_date_ffr)) %>%
  filter(date <= max_date_ffr) %>%
  rename(tr_mid_h0 = tr_mid) %>%
  inner_join(ffr_set_h6, "date")

forecast_set <- ffr_set_first_day %>%
  filter(between(date, date("2022-03-01"), max_date_ffr)) %>%
  rename(tr_mid_h0 = tr_mid) %>%
  left_join(ffr_set_h6, "date") %>%
  filter(is.na(tr_mid_h6)) %>%
  mutate(set = "forecast")

```


# Create train and test partition


```{r}

set.seed(3)


ind <- createDataPartition(full_set$tr_mid_h6, 1, 0.7, FALSE)

train_set <- full_set[ind, ] %>%
  mutate(set = "train")

test_set <- full_set[-ind, ] %>%
  mutate(set = "test")

h0_set <- rbind(train_set, test_set, forecast_set) %>%
  arrange(date)

# Minimum date from h0 set
min_date_h0 <- min(h0_set$date)
# Maximum date from h0 set
max_date_h0 <- max(h0_set$date)

cat("Minimum date: ", as.character(min_date_h0), fill = TRUE)
cat("Maximum date: ", as.character(max_date_h0), fill = TRUE)

h0_set

```


# Process FFR set with time lags
 

```{r}

ffr_set_lag6 <- ffr_set_first_day %>%
  filter(between(date, min_date_h0 %m-% months(6), max_date_h0 %m-% months(6))) %>%
  mutate(date = date %m+% months(6)) %>%
  rename(tr_mid_lag6 = tr_mid)

ffr_set_lag3 <- ffr_set_first_day %>%
  filter(between(date, min_date_h0 %m-% months(3), max_date_h0 %m-% months(3))) %>%
  mutate(date = date %m+% months(3)) %>%
  rename(tr_mid_lag3 = tr_mid)

ffr_set_lag2 <- ffr_set_first_day %>%
  filter(between(date, min_date_h0 %m-% months(2), max_date_h0 %m-% months(2))) %>%
  mutate(date = date %m+% months(2)) %>%
  rename(tr_mid_lag2 = tr_mid)

ffr_set_lag1 <- ffr_set_first_day %>%
  filter(between(date, min_date_h0 %m-% months(1), max_date_h0 %m-% months(1))) %>%
  mutate(date = date %m+% months(1)) %>%
  rename(tr_mid_lag1 = tr_mid)

```


# Process CPI set with time lags


```{r}

cpi_set_lag16 <- cpi_set %>%
  filter(between(date, min_date_h0 %m-% months(16), max_date_h0 %m-% months(16))) %>%
  mutate(date = date %m+% months(16)) %>%
  rename(cpi_lag16 = cpi)

cpi_set_lag12 <- cpi_set %>%
  filter(between(date, min_date_h0 %m-% months(12), max_date_h0 %m-% months(12))) %>%
  mutate(date = date %m+% months(12)) %>%
  rename(cpi_lag12 = cpi)

cpi_set_lag6 <- cpi_set %>%
  filter(between(date, min_date_h0 %m-% months(6), max_date_h0 %m-% months(6))) %>%
  mutate(date = date %m+% months(6)) %>%
  rename(cpi_lag6 = cpi)

```


# Plot CPI vs. FFR


```{r}

ffr_vs_cpi_set <- h0_set %>%
  inner_join(cpi_set_lag16, "date") %>%
  inner_join(cpi_set_lag12, "date") %>%
  inner_join(cpi_set_lag6, "date") %>%
  select(-tr_mid_h6, -set) %>%
  gather(key = "index", value = "value", -date)

ffr_vs_cpi_set %>%
  ggplot(aes(x = date, y = value, color = index, linetype = index)) +
  geom_line(linewidth = 1) +
  labs(
    title = "CPI vs. FFR",
    x = "Date",
    y = "Rate %",
    color = "Index",
    linetype = ""
  ) + # Titles
  theme_classic() + # Main theme
  qa_dark + # Add theme settings
  theme(axis.text.x = element_text(angle = 90), legend.position = "right") +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = "3 months") + # Date labels scale
  scale_color_manual(values = c("tr_mid_h0" = color_pallete[3],
                                "cpi_lag16" = color_pallete[1],
                                "cpi_lag12" = color_pallete[2],
                                "cpi_lag6" = color_pallete[7]
                                ),
                     labels = c("tr_mid_h0" = "FFR mid point",
                                "cpi_lag16" = "CPI lag 16",
                                "cpi_lag12" = "CPI lag 12",
                                "cpi_lag6" = "CPI lag 6")) +
  scale_linetype_manual(values = c("tr_mid_h0" = "solid",
                                   "cpi_lag16" = "dotted",
                                   "cpi_lag12" = "solid",
                                   "cpi_lag6" = "dotted"),
                        labels = NULL)


```


# Scatter plots of time lagged variables


```{r}

# Include FFR and CPI lags variables
h0_set <- h0_set %>%
  inner_join(ffr_set_lag6, "date") %>%
  inner_join(ffr_set_lag3, "date") %>%
  inner_join(ffr_set_lag2, "date") %>%
  inner_join(ffr_set_lag1, "date") %>%
  inner_join(cpi_set_lag16, "date") %>%
  inner_join(cpi_set_lag12, "date") %>%
  inner_join(cpi_set_lag6, "date")

name_X <- colnames(h0_set)[!(colnames(h0_set) %in% c("date", "tr_mid_h6", "set"))]

name_Y <- "tr_mid_h6"

p_scatter1 <- lapply(name_X, function(x) {
  h0_set %>%
    filter(set %in% c("train", "test")) %>%
    ggplot(aes(x = !!as.symbol(x), y = !!as.symbol(name_Y))) +
    geom_point(color = color_pallete[2], size = 4) +
    theme_classic() + # Main theme
    qa_dark + # Add theme settings
    labs(
      x = x,
      y = name_Y
    ) +
    theme(
      axis.text.x = element_text(angle = 0)
    )
})

wrap_plots(p_scatter1)



```


# Calculating moving averages for FFR


```{r}

ffr_set_ma6 <- ffr_set_first_day %>%
  mutate(tr_mid_ma6 = moving_avg(tr_mid, 6)) %>%
  filter(between(date, min_date_h0, max_date_h0)) %>%
  select(-tr_mid)

ffr_set_ma3 <- ffr_set_first_day %>%
  mutate(tr_mid_ma3 = moving_avg(tr_mid, 3)) %>%
  filter(between(date, min_date_h0, max_date_h0)) %>%
  select(-tr_mid)

ffr_set_ma2 <- ffr_set_first_day %>%
  mutate(tr_mid_ma2 = moving_avg(tr_mid, 2)) %>%
  filter(between(date, min_date_h0, max_date_h0)) %>%
  select(-tr_mid)

```


# Include new variables in FFR set and generate scatter plots


```{r}

h0_set <- h0_set %>%
  inner_join(ffr_set_ma6, "date") %>%
  inner_join(ffr_set_ma3, "date") %>%
  inner_join(ffr_set_ma2, "date")

name_X <- colnames(h0_set)[!(colnames(h0_set) %in% c("date", "tr_mid_h6", "set"))]

p_scatter2 <- lapply(name_X, function(x) {
  h0_set %>%
    filter(set %in% c("train", "test")) %>%
    ggplot(aes(x = !!as.symbol(x), y = !!as.symbol(name_Y))) +
    geom_point(color = color_pallete[2], size = 4) +
    theme_classic() + # Main theme
    qa_dark + # Add theme settings
    labs(
      x = x,
      y = name_Y
    ) +
    theme(
      axis.text.x = element_text(angle = 0)
    )
})

wrap_plots(p_scatter2)


```


# Create log transformed variables


```{r}

log_transformed <- apply(h0_set[, name_X], 2, function(x) {
  log(x)
})
colnames(log_transformed) <- paste0("log_", colnames(log_transformed))


h0_set <- h0_set %>%
  cbind(log_transformed)

name_X_log <- colnames(log_transformed)

p_scatter3 <- lapply(name_X_log, function(x) {
  h0_set %>%
    filter(set %in% c("train", "test")) %>%
    ggplot(aes(x = !!as.symbol(x), y = !!as.symbol(name_Y))) +
    geom_point(color = color_pallete[2], size = 4) +
    theme_classic() + # Main theme
    qa_dark + # Add theme settings
    labs(
      x = x,
      y = name_Y
    ) +
    theme(
      axis.text.x = element_text(angle = 0)
    )
})

wrap_plots(p_scatter3)


```


# Analyse the distribution of the original variables


```{r}


h0_set %>%
  select(all_of(name_X)) %>%
  gather(key = "variable", value = "value") %>%
  ggplot(aes(x = value)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 5, fill = color_pallete[2], color = "white") +
  scale_fill_manual(values = color_pallete) +
  facet_wrap(~ variable, scale = "free") +
  theme_classic() + # Main theme
  labs(
    x = "Rate",
    y = "Freq"
  ) + # Titles
  qa_dark + # Add theme settings
  theme(
    strip.text = element_text(color = "white"),
    axis.text.x = element_text(angle = 0)
  )


```


# Analyse the distribution of the transformed variables


```{r}


h0_set %>%
  select(all_of(name_X_log)) %>%
  gather(key = "variable", value = "value") %>%
  ggplot(aes(x = value)) +
  geom_histogram(position = "identity", alpha = 0.5, bins = 5, fill = color_pallete[2], color = "white") +
  scale_fill_manual(values = color_pallete) +
  facet_wrap(~ variable, scale = "free") +
  theme_classic() + # Main theme
  labs(
    x = "Rate",
    y = "Freq"
  ) + # Titles
  qa_dark + # Add theme settings
  theme(
    strip.text = element_text(color = "white"),
    axis.text.x = element_text(angle = 0)
  )


```


# Create a dummy variable to capture 0 variance periods


```{r}

variance_dummy_lag2 <- ffr_set_first_day %>%
  mutate(vd_tr_mid_lag2 = dummy_of_variance_0(tr_mid, 2)) %>%
  filter(between(date, min_date_h0, max_date_h0)) %>%
  select(-tr_mid)

```



# Create a dummy variable to capture relative changes


```{r}

change_dummy_lag2 <- ffr_set_first_day %>%
  mutate(cd_tr_mid_lag2 = dummy_of_change(tr_mid, 2, 0.2)) %>%
  filter(between(date, min_date_h0, max_date_h0)) %>%
  select(-tr_mid)

change_dummy_lag2

```


# Include the dummy variables in the dataset


```{r}

h0_set <- h0_set %>%
  inner_join(variance_dummy_lag2, "date") %>%
  inner_join(change_dummy_lag2, "date")

```


# Correlation matrix


```{r}

name_X_selected <- c("log_tr_mid_h0", "log_tr_mid_lag1", "log_cpi_lag16", "log_cpi_lag12", "log_tr_mid_ma6", "log_tr_mid_ma3", "log_tr_mid_ma2", "vd_tr_mid_lag2", "cd_tr_mid_lag2")

cor_matrix <- cor(h0_set[h0_set$set %in% c("train", "test"), c(name_X_selected, name_Y)], method = "spearman")

p_cor <- ggcorrplot(cor_matrix,type = "lower",
           lab = TRUE,
           lab_col = "black",
           outline.color = "white",
           colors = viridis(4),
           lab_size = 3.5,
           title = "Correlation Matrix",
           legend.title = "")

p_cor <- p_cor +
  theme_classic() +
  theme(
    plot.background = element_rect(fill = "black"),
    axis.text.x = element_text(angle = 90, hjust = 1, color = "white"),
    axis.text.y = element_text(color = "white"),
    plot.title = element_text(hjust = 0.5, color = "white"),
    legend.background = element_blank(),
    legend.key = element_blank(),
    legend.text = element_text(color = "white"),
    legend.title = element_text(color = "white"),
    panel.background = element_rect(fill = NA)
   )

p_cor



```


# Linear model


```{r}

# Filter train set
train_set <- h0_set[h0_set$set %in% c("train", "test"), ]

# Filter test set
# test_set <- h0_set[h0_set$set == "test", ]

mod <- lm(tr_mid_h6 ~ cd_tr_mid_lag2 + log_tr_mid_ma3, data = train_set)

# Observed values in train set
y <- train_set$tr_mid_h6

# Summary statistics of the model
summary(mod)
# Predicted values in train set
y_hat = predict(mod, train_set)
# Obtain residuals
res <- y - y_hat

```

# Performance indicators


```{r}

performance_ind <- tibble(
  "Dataset" = "train",
  `Multiple R-squared` = r_squared(y, y_hat),
  `Adjusted R-squared` = adjusted_r_squared(y, y_hat, 2),
  `RMSE` = rmse(y, y_hat)
)

performance_ind %>%
  mutate(
    `Multiple R-squared` = percent((`Multiple R-squared`)),
    `Adjusted R-squared` = percent((`Adjusted R-squared`)),
    RMSE = as.character(round(RMSE, 4))
  )


```


# Distribution of residuals


```{r}

# Distribution of residuals
ggplot() +
geom_histogram(aes(x = res, y = after_stat(count) * 100 / sum(count)), color = "white", fill = color_pallete[3], bins = 5) +
theme_classic() + # Main theme
labs(
  title = "Residuals - Histogram",
  x = "Residuals",
  y = "Freq %"
) + # Titles
qa_dark + # Add theme settings
theme(axis.text.x = element_text(angle = 0))

```


# Normality of residuals


```{r}

ggplot() +
stat_qq(aes(sample = res), color = color_pallete[3], size = 4, alpha = 0.6) +
stat_qq_line(aes(sample = res), color = color_pallete[2], linewidth = 1) +
theme_classic() + # Main theme
qa_dark + # Add theme settings
labs(
  x = "Normal theoretical quantiles",
  y = "Residuals",
  title = "Residuals - Q-Q Plot"
) +
theme(
    axis.text.x = element_text(angle = 0),
    panel.grid.major = element_line(color = "white", linewidth = 0.25, linetype = "dotted"),
    panel.grid.minor = element_line(color = "white", linewidth = 0.25, linetype = "dotted")
  )


```

# Variance and non-linearity check


```{r}

ggplot() +
geom_point(aes(x = y_hat, y = res), color = color_pallete[3], size = 4, alpha = 0.6) +
geom_hline(yintercept = 0, color = color_pallete[2], linewidth = 1) +
theme_classic() + # Main theme
qa_dark + # Add theme settings
labs(
  x = "Fitted values",
  y = "Residuals",
  title = "Residuals vs. Fitted"
) +
theme(
    axis.text.x = element_text(angle = 0),
    panel.grid.major = element_line(color = "white", linewidth = 0.25, linetype = "dotted"),
    panel.grid.minor = element_line(color = "white", linewidth = 0.25, linetype = "dotted")
  ) +
scale_x_continuous(breaks = seq(0, 6 , 0.5))

```


# Homoscedasticity check


```{r}

ggplot() +
geom_point(aes(x = y_hat, y = sqrt(abs(res))), color = color_pallete[3], size = 4, alpha = 0.6) +
theme_classic() + # Main theme
qa_dark + # Add theme settings
labs(
  x = "Fitted values",
  y = "Square root of residuals",
  title = "Standardized Residuals vs. Fitted"
) +
theme(
    axis.text.x = element_text(angle = 0),
    panel.grid.major = element_line(color = "white", linewidth = 0.25, linetype = "dotted"),
    panel.grid.minor = element_line(color = "white", linewidth = 0.25, linetype = "dotted")
  ) +
scale_x_continuous(breaks = seq(0, 6 , 0.5))

```


# Statistical tests


```{r}

stats_tests <- tibble(
  test = c("Normality of residuals - Shapiro-Wilk", "Variance of residuals - Breush-Pagan", "Autocorrelation of residuals - Durbin-Watson"),
  statistic = c(shapiro.test(res)$statistic, ncvTest(mod)$ChiSquare, durbinWatsonTest(mod)$dw),
  `p-value` = c(shapiro.test(res)$p.value, ncvTest(mod)$p, durbinWatsonTest(mod)$p),
  h0 = c("Residuals are normally distributed", "The variance of residuals is constant", "There is no first-order autocorrelation in the residuals"),
  result = ifelse(`p-value` > 0.05, "Not rejected", "Rejected")
)

stats_tests %>%
  mutate(
    `p-value` = percent(`p-value`),
    statistic = as.character(round(statistic, 4))
  )

```


# Autocorrelation function (ACF)


```{r}

# ACF values
acf_res <- as.numeric(acf(res, plot = FALSE)$acf)

# Standard devitation of residuals
stdv_acf <- qnorm(1 - 0.05 / 2) / sqrt(length(res))

# Create a data frame with the ACF values
acf_res <- tibble(acf_res) %>%
  mutate(lag = as.factor(seq(0, length(acf_res) - 1, 1)))

# Plot the autocorrelation function
acf_res %>%
  ggplot(aes(x = lag, y = acf_res)) +
  geom_bar(stat = "identity", width = 0.2, fill = color_pallete[3]) +
  geom_hline(yintercept = 0, linetype = "solid", color = "white", linewidth = 1) +
  geom_hline(yintercept = stdv_acf, linetype = "dashed", color = color_pallete[2], linewidth = 1) +
  geom_hline(yintercept = -stdv_acf, linetype = "dashed", color = color_pallete[2], linewidth = 1) +
  theme_classic() +
  qa_dark +
  theme(
    axis.text.x = element_text(angle = 0)
  ) +
  labs(
    title = "Autocorrelation Function",
    x = "Lag",
    y = "Autocorrelation - lag 1"
  )
  

```


# Predicted vs. Observed


```{r}

data.frame(
  y_hat = y_hat,
  y = y
) %>%
  ggplot(aes(x = y_hat, y = y)) +
  geom_abline(color = color_pallete[2], linewidth = 1) +
  geom_point(color = color_pallete[3], size = 4, alpha = 0.6) +
  theme_classic() + # Main theme
  qa_dark + # Add theme settings
  labs(
    x = "Y hat",
    y = "Y",
    title = "Predicted vs. Observed"
  ) +
  theme(
      axis.text.x = element_text(angle = 0),
      panel.grid.major = element_line(color = "white", linewidth = 0.25, linetype = "dotted"),
      panel.grid.minor = element_line(color = "white", linewidth = 0.25, linetype = "dotted")
    )


```


# Confidence intervals for predictions


```{r}

intervals <- predict(mod, interval = "confidence", newdata = h0_set, level = 0.99)

h0_set$y_hat <- intervals[, "fit"]
h0_set$lwr <- intervals[, "lwr"]
h0_set$upr <- intervals[, "upr"]

```


# Forecasts + Confidence Intervals


```{r}

h0_forecast_set <- h0_set %>%
  mutate(
    tr_mid_h6 = ifelse(is.na(tr_mid_h6), y_hat, tr_mid_h6),
    date = date %m+% months(6),
    forecast = ifelse(set == "forecast", "Y", "N")
  )

h0_forecast_set %>%
  ggplot(aes(x = date, ymin = lwr, ymax = upr)) +
  geom_ribbon(alpha = 0.2, fill = color_pallete[1]) +
  geom_line(aes(x = date, y = tr_mid_h6, color = "Observed", alpha = forecast), linewidth = 1) +
  geom_line(aes(x = date, y = y_hat, color = "Predicted"), linewidth = 1, alpha = 0.8, linetype = "dashed") +
  theme_classic() + # Main theme
  labs(
    title = "FFR's Mid Point - Forecast",
    x = "Date",
    y = "Mid Point %",
    color = "",
    alpha = ""
  ) + # Titles
  qa_dark +
  scale_x_date(date_labels = "%Y-%m-%d", breaks = "2 months") +
  scale_color_manual(values = c("Observed" = color_pallete[3], "Predicted" = color_pallete[1])) +
  scale_alpha_manual(values = c("Y" = 0, "N" = 0.8), labels = NULL) +
  theme(
    panel.grid.major = element_line(color = "white", linewidth = 0.25, linetype = "dotted"),
    panel.grid.minor = element_line(color = "white", linewidth = 0.25, linetype = "dotted")
  )

```

# Display forecasts


```{r}

h0_forecast_set %>%
  filter(forecast == "Y") %>%
  select(date, y_hat, lwr, upr)

```


